\documentclass[10pt, letterpaper]{article}

% ATS-SAFE: Use Helvetica (Arial equivalent) — zero ligature/encoding issues
\usepackage{fontenc}
\usepackage{pifont}

\usepackage[margin=0.4in, top=0.4in, bottom=0.4in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{microtype}

% Kill all paragraph spacing
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

% ── COMMANDS ──────────────────────────────────────────────────────────────────

% Section header: small-caps effect via \textbf + \large, ruled underneath
\newcommand{\ressection}[1]{%
  \vspace{16pt}%
  {\large\textbf{#1}}%
  \vspace{0pt}\newline%
  \rule{\linewidth}{0.4pt}%
  \vspace{0pt}%
}

% Company name (left) + location (right) — single paragraph, no table
\newcommand{\rescompany}[2]{%
  \vspace{5pt}%
  {\textbf{#1}\hfill\textbf{#2}}\par%
}

% Role (left, italic) + dates (right) — single paragraph, no table
\newcommand{\resrole}[2]{%
  {\textit{#1}\hfill #2}\par\vspace{2pt}%
}

% Project / app title line
\newcommand{\resapp}[1]{%
  \vspace{3pt}{\small\textbf{#1}}\par\vspace{0pt}%
}

% Tech stack — italic label, normal value
\newcommand{\restech}[1]{%
  {\small\textit{Tech: }#1}\par\vspace{1pt}%
}

% Bullet list — standard hyphen bullets, ATS-safe
\newenvironment{resbullets}{%
  \begin{itemize}[
    leftmargin=1.4em,
    itemsep=0pt,
    parsep=0pt,
    topsep=2pt,
    label={-}
  ]
  \small
}{%
  \end{itemize}%
}

% ── SKILLS TABLE: single-column, no tabular ──────────────────────────────────
% Each row is just bold label + colon + value on one line
\newcommand{\skillrow}[2]{%
  {\small\textbf{#1:} #2}\par\vspace{1pt}%
}

\pagestyle{empty}

\begin{document}

% ── HEADER ────────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\textbf{Chirag Bhaiji}}\\[4pt]
  {\small
  +91-86052 01092 \,|\,
  \href{mailto:chiragbhaiji@gmail.com}{chiragbhaiji@gmail.com} \,|\,
  \href{https://linkedin.com/in/chiragbhaiji}{linkedin.com/in/chiragbhaiji} \,|\,
  \href{https://github.com/chiragbhaiji}{github.com/chiragbhaiji}%
  }
\end{center}

% ── SUMMARY ───────────────────────────────────────────────────────────────────
\ressection{Summary}
{\small Senior mobile engineer with over a decade of experience shipping production-grade React Native,
Swift, and React.js applications across E-commerce, Healthcare, Blockchain, and SaaS. Proven track record
leading mobile engineering teams, architecting scalable white-label mobile platforms, and delivering
measurable performance and engagement improvements. Deep focus on clean architecture, CI/CD,
AI-assisted development workflows, and code quality.}

% ── TECHNICAL SKILLS ──────────────────────────────────────────────────────────
\ressection{Technical Skills}
\skillrow{Languages}{JavaScript (ES6+), TypeScript, Swift}
\skillrow{Mobile and Web}{React Native, React.js, Redux, Redux Toolkit, Zustand, React Query, Reanimated, Web3.js, Lottie}
\skillrow{Testing and CI/CD}{Jest, React Testing Library, XCTest, SonarQube, Fastlane, GitHub Actions, Firebase App Distribution}
\skillrow{Monitoring and Analytics}{Sentry, BugSnag, Firebase Crashlytics, AppDynamics, Mixpanel, CleverTap, GrowthBook, UserExperior, Fullstory}
\skillrow{Databases and APIs}{Realm, SQLite, Firebase (RTDB/Firestore), Salesforce SDK, REST API, Socket.io, Razorpay, Apple IAP, Apple Health}
\skillrow{Tools}{Xcode, Android Studio, Flipper, Figma, VS Code, Cursor, Claude, ChatGPT}
\skillrow{Practices}{Agile, Scrum, Code Review, AI-Assisted Development, App Store and Google Play Release Management}

% ── EXPERIENCE ────────────────────────────────────────────────────────────────
\ressection{Experience}

% PwC ──────────────────────────────────────────────────────────────────────────
\rescompany{PwC Acceleration Center}{Pune, India (Remote)}
\resrole{Manager -- React Native}{Apr 2025 -- Feb 2026}
\resapp{Savvy | Enterprise field-operations app for PepsiCo}
\restech{React Native, TypeScript, Redux Toolkit, Salesforce SDK, AppDynamics, Fastlane, GitHub Actions, Cursor}
\begin{resbullets}
  \item Led the React Native team to ship 5 features within a cross-functional delivery structure.
  \item Bridged offshore team, PwC leadership, and PepsiCo stakeholders, resolving blockers and keeping sprint delivery on track.
  \item Resolved 10+ critical production issues to keep the app stable and clear the defect backlog.
  \item Defined a reusable AI review prompt used team-wide, making AI the first pass on every PR and freeing engineers for higher-order feedback.
  \item Used Cursor to debug a large legacy codebase with limited documentation, analyzing huge log files, cutting root cause identification time across production issues.
  \item Created onboarding docs and developer guides to cut new React Native ramp-up time from 2+ weeks to approximately 1 week.
\end{resbullets}

% Thrive ───────────────────────────────────────────────────────────────────────
\rescompany{Thrive Now (Hashtag Loyalty)}{Mumbai, India (Remote)}
\resrole{Senior React Native Developer}{Feb 2024 -- Dec 2024}
\resapp{Thrive | Food discovery and ordering app}
\restech{React Native, TypeScript, Redux Toolkit, React Query, Reanimated, Sentry, Firebase, Cursor, GitHub Copilot, Claude, Notion AI}
\begin{resbullets}
  \item Designed and built Rewards, Customer Feedback, and Personalized Ratings end-to-end, driving a 30\% increase in user engagement.
  \item Used Cursor, GitHub Copilot, and Claude daily, cutting root cause identification time in production issues by 50--60\%.
  \item Used Notion AI to document app flows and write ticket descriptions, reducing clarification rounds and improving sprint clarity.
  \item Replaced a third-party Carousel with a self created component using Reanimated, cutting RAM usage by 40--50\% and improving scroll performance.
  \item Led a codebase-wide refactor that reduced technical debt by 20\%, improving maintainability, security, and code review speed.
  \item Enabled Sentry to track performance and uploaded debug symbols to reduce stack trace resolution time from days to hours.
\end{resbullets}

% EPAM ─────────────────────────────────────────────────────────────────────────
\rescompany{EPAM Systems}{Pune, India}
\resrole{Lead Software Developer}{Jul 2023 -- Feb 2024}
\resapp{Bloom - IQVIA | Patient-centric app for remote clinical trial participation}
\restech{React Native, TypeScript, Redux Toolkit, React Query, Firebase, REST API, deep linking}
\begin{resbullets}
  \item Delivered the Surveys module - the app\textquotesingle{}s most business-critical feature - end-to-end within 5 days of joining, directly unblocking a stalled release milestone.
  \item Diagnosed broken deep link flows for email verification and password reset, then built a generalized integration pattern that scales to all future features.
  \item Built the Rewards feature and refactored a fragmented healthcare provider form into a single composable component supporting 4 distinct usage scenarios.
\end{resbullets}

% BigBinary ────────────────────────────────────────────────────────────────────
\rescompany{BigBinary}{Pune, India (Remote)}
\resrole{Software Engineer}{Jun 2021 -- Jul 2023}

\resapp{Head On: Stress and Anxiety | Psychologist-designed emotional well-being app (iOS and Android)}
\restech{React Native, TypeScript, Reanimated, Lottie, Apple IAP, Firebase, push notifications}
\begin{resbullets}
  \item Built the In-App Purchases flow and push notification system, enabling monetisation and re-engagement that improved daily active users and retention.
  \item Built a reusable library of animated custom UI components with Reanimated and Lottie, powering the app\textquotesingle{}s micro-interaction experience across all core screens.
\end{resbullets}

\resapp{Turtle Method | Nutrition and mindset coaching app for fat loss and fitness (iOS and Android)}
\restech{React Native, TypeScript, Apple Health, Fitbit API, Garmin API, Firebase}
\begin{resbullets}
  \item Automated 90\% of manual coach workflows - scheduling, tracking, and reporting - increasing client capacity per coach and driving platform adoption.
  \item Integrated Apple Health, Fitbit, and Garmin APIs for automatic biometric syncing, eliminating manual data entry and enabling real-time progress tracking for coaches.
\end{resbullets}

\resapp{Neeto Suite | SaaS productivity apps - neetoInvoice, neetoCal, neetoDesk}
\restech{React Native, TypeScript, neetoUI-RN, React Query, Redux Toolkit, Fastlane, Firebase App Distribution}
\begin{resbullets}
  \item Built 3 of 6 apps in the Neeto suite from the ground up; automated iOS and Android release pipelines via Fastlane, removing manual distribution steps.
  \item Ran competitive analysis to surface feature gaps that were directly incorporated into the product roadmap.
\end{resbullets}

% Deqode ───────────────────────────────────────────────────────────────────────
\rescompany{Deqode Solutions}{Indore, India}
\resrole{Team Lead / Senior Solution Engineer}{Apr 2017 -- May 2021}

\resapp{PumaPay | DeFi payment protocol for peer-to-peer transactions}
\restech{Swift, React Native, Web3.js, Ethereum, Ruby, white-label architecture, REST API}
\begin{resbullets}
  \item Joined as sole founding engineer; shipped the first production version, then grew and led the engineering team from 0 to 15 engineers.
  \item Rebuilt the legacy hybrid app from scratch in native Swift, then architected it as a white-label platform delivering full per-client customisation within a one-month window.
  \item Wrote a Ruby script to automate per-client theme and feature generation, eliminating manual setup on each new wallet deployment.
\end{resbullets}

\resapp{Patientory | Decentralised health record app built on blockchain (iOS)}
\restech{Swift, Hyperledger, IPFS, blockchain SDK, REST API}
\begin{resbullets}
  \item Designed and built a Swift SDK for Hyperledger blockchain interaction from scratch, forming the core integration layer between the app and the network.
  \item Collaborated with the backend team to integrate IPFS, enabling distributed health record storage and removing the single point of failure of centralised file hosting.
\end{resbullets}

% Webonise ─────────────────────────────────────────────────────────────────────
\rescompany{Webonise Lab (now Haptiq)}{Pune, India}
\resrole{Software Developer}{Jun 2014 -- Mar 2017}
\resapp{Red Hat Partner Connect | B2B matchmaking app for contract-based partnerships}
\restech{React Native, JavaScript, Socket.io, REST API, OOP design patterns}
\begin{resbullets}
  \item Built a real-time partner chat feature using Socket.io, and refactored a screen with 20+ dynamic form fields using OOP patterns, reducing complexity and maintenance overhead.
  \item Partnered with business analysts and clients to translate ambiguous requirements into scoped technical solutions, reducing rework from unclear specs.
\end{resbullets}

% ── EDUCATION ─────────────────────────────────────────────────────────────────
\ressection{Education}
\rescompany{RGPV University}{Madhya Pradesh, India}
{\small\textit{Bachelor of Engineering in Computer Science}\hfill 2010 -- 2014}

\end{document}